## Make 2Kb Intergenic regions

The intergenic regions that I made, which are detailed in  `cleanedFlybaseBetweenGenes_17July2017.BED` are not able to actually be lifted from the genome, likely becasue the regions are so large.

I want to find random 2kb regions and then filter if they overlapp with the kvon regions. 

```{r}
library(GenomicRanges)
library(rtracklayer)
```

## To Do

- [x] Retrieve random number between start and end 
- [ ] Choose random regions and allow resampling
- [x] You go up or down 2kb
  - [x] Is the region at least 2KB
    - yes, continue
    - no, don't use
   - [x] Make sure it doesn't hit the start or end
  - [x]I guess you can just go 2KB in each region.
- [ ] Make sure it does not overlapp with previous Kvon data sets.
- [ ] Make sure it does not overlap in promoter regions ect.

## Finding the regions

Rewrite the bed file. This is mostly to reformat for uses ranges, but I didn't end up using ranges.

```{r}
inter_regions_bed <- read.table("../../cleanedFlybaseBetweenGenes_17July2017.BED")

# making new and writing out so that the import function works. The main problem was that the "score" column is supposed to be a number.

colnames(inter_regions_bed) <- c("seqnames", "starts", "ends", "names", "scores", "strands")
inter_regions_bed$scores <- 0

#write.table(inter_regions_bed, "../../rearrange_cleanedFlybaseBetweenGenes_17July2017.BED", col.names=F,row.names=F,sep="\t",quote=F)
```

## Randomization

- [ ] The ifelse statement is not working.

```{r}
## prepare dataset
inter_regions <- subset(inter_regions_bed, select = -c(scores, strands))
inter_regions$size <- inter_regions$ends - inter_regions$starts

## Make new column start and end columns that start and end 2kb in
## Start
ifelse(inter_regions$size > 2000, inter_regions$starts_2kb <- inter_regions$starts  + 2000, "NA")

## Ends
ifelse(inter_regions$size > 2000, inter_regions$ends_2kb <- inter_regions$ends  + 2000, "NA")

## Pick random number
inter_regions$random_start <- 1

# Pick a random number between the ranges, in each range
for (i in 1:nrow(inter_regions)) {
  n <- sample(inter_regions$starts_2kb[i]:inter_regions$ends_2kb[i], 1)
  inter_regions$random_start[i] <- n
}

# Make a vector of random 0 and 1s
# To use when isolating randomly choosing upstream or 
# downstream of random number
inter_regions$x <- sample(c(0,1), replace = TRUE, size = nrow(inter_regions))

## Check
summary(as.factor(inter_regions$x))

head(inter_regions)

# This is not working correctly
df$food %in% veg

inter_regions$random_end <- ifelse(inter_regions$x == 1, 
                                   inter_regions$random_start  + 2000,
                                   inter_regions$random_start  - 2000)

head(inter_regions, 50)
```

Now switch the column values depending on if we went upstream or downstream.
```{r}
## Now some of the starts start after some of the ends
## I need to write something that asks:
## If the random_end column is less than the random_start column, switch the values.

## Check
test1 <- inter_regions$random_end - inter_regions$random_start
plot(test1)
summary(test1)

inter_regions$random_start_2 <- ifelse(inter_regions$random_start < inter_regions$random_end, inter_regions$random_start, inter_regions$random_end)

inter_regions$random_end_2 <- ifelse(inter_regions$random_start > inter_regions$random_end, inter_regions$random_start, inter_regions$random_end)

test <- inter_regions$random_end_2 - inter_regions$random_start_2   
plot(test)
```

Make BED file output for 

```{r}
# 6 columns
# chr (ex. chr2L), start, end, names, score (ex. all "score"), strand (ex. all "+")

colnames(inter_regions)
for_new_bed <- inter_regions[,c(1,11,12,4)]
head(for_new_bed) 

for_new_bed$seqnames <- sub("^", "chr", for_new_bed$seqnames)

for_new_bed$score <- "score"
for_new_bed$strand <- "+"

write.table(for_new_bed,"../../1.random_intergenic_regions_1August2017.bed",col.names=F,row.names=F,sep="\t",quote=F)
```

## Learning Ranges

```{r}
# To use with ranges.
b <- import("../../rearrange_cleanedFlybaseBetweenGenes_17July2017.BED", format="bed")

```