## Make 2Kb Intergenic regions

Purpose: I want to find random 2,000 bp (length) regions that will act as "control" for statistical tests. Are the properties that are found in random 2000 bp regions different then those that are represented with the kvon dataset. 

```{r}
## Possible Libraries that might be useful
library(GenomicRanges)
library(rtracklayer)
```

## To Do

- [ ] Retrieve random number between start and end 
- [ ] Choose random regions and allow resampling
- [ ] You go up or down 2000bp
  - [ ] Is the region at least 2000bp 
    - yes, continue
    - no, don't use
   - [ ] Make sure it doesn't hit the start or end
- [ ] Non - overlapping regions
- [ ] Make sure it does not overlapp with previous Kvon data sets.
- [ ] Make sure it does not overlap in promoter regions ect (not yet).
- [ ] Number of regions random regions = 7,500
- [ ] Visualize

## Finding the regions

Rewrite the bed file. This is mostly to reformat for use with ranges.

```{r}
inter_regions_bed <- read.table("../data/input/cleanedFlybaseBetweenGenes_17July2017.BED")

## rename columns and clean
colnames(inter_regions_bed) <- c("seqnames", "starts", "ends", "names", "scores", "strands")
inter_regions_bed$scores <- 0

## write.table(inter_regions_bed, "../data/output/rearrange_cleanedFlybaseBetweenGenes_20March2018.BED", col.names=F,row.names=F,sep="\t",quote=F)

## prepare dataset
inter_regions <- subset(inter_regions_bed, select = -c(scores, strands))
inter_regions$size <- inter_regions$ends - inter_regions$starts
```

## About data

- `seqnames`: chromosome
- `starts`: start of intergenic region
- `ends`: end of intergeneic region
- `size`: size of intergenic region

## Find random 2kb regions.

```{r}
head(inter_regions)
levels(inter_regions$seqnames)
```